Quantitative Auditing of AI Fairness with Differentially Private Synthetic Data

### 2024-12-14 paper/paper.tex
minor

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Quantitative Auditing of AI Fairness with differentially private Synthetic Data}

@@

In the COMPAS example, the sensitive attribute is sex and the protected group is female, the protected group predicate would be $S := r(sex) = Female$; prediction is if a person will re-offend $\hat{Y} := \mathcal{M}_{recid}(r)$ where $M$ is the model's prediction of row $r$; ground truth is whether a person does re-offend $Y := r(recid)$. These can be easily implemented in Python as a comparison function.

>>>>

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Quantitative Auditing of AI Fairness with Differentially Private Synthetic Data}

@@

In the COMPAS example, the sensitive attribute is sex and the protected group is female, the protected group predicate would be $S := r(sex) = Female$; prediction is if a person will re-offend $\hat{Y} := \mathcal{M}_{recid}(r)$ where $\mathcal{M}$ is the model's prediction of row $r$; ground truth is whether a person does re-offend $Y := r(recid)$. These can be easily implemented in Python as a comparison function.
